### 2011-01-26 paper/introduction.tex

@@

\editbox{Outline \\
 - Why gait learning is cool \\
 - Gait learning has been done before, in simulation and on hardware (cite, cite, cite) \\
 - HyperNEAT has been used to evolve gaits before in sim (cite, ...) \\
 - Here, we do two cool things for the first time: \\
 - - evolve HN in hardware \\
 - - compare it to other learning methods on the same hardware.}

>>>>

\acmFig{robot_close.jpg}{1}{The 3D printed quadruped robot used for
  this study.}

@@

%\editbox{Outline \\
% - Why gait learning is cool \\
% - Gait learning has been done before, in simulation and on hardware (cite, cite, cite) \\
% - HyperNEAT has been used to evolve gaits before in simulation~{clune2009evolving, clune2011performance, clune2009hybrid}, and it worked well in part because the gaits were regular, raising the question of whether this high performance was just because the gaits were regular? We test this hypothesis by comparing HyperNEAT to traditional machine learning methods biased towards regular gaits.  \\
% - Here, we do two cool things for the first time: \\
% - - evolve HN in hardware \\
% - - compare it to other learning methods on the same hardware.}
